---
title: "Participant Filtering"
author: "Micah E. Hirsch"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Document Purpose

The purpose of this document is to filter out the participants to be included in this sensor effects project from the larger study database. While we do not provide access to the raw participant inventory here, the script blocks below demonstrate how we identified participants to include in this analysis. The primary criteria we needed was audio recordings from before sensor placement, the conversational sample with sensors on, and recordings after sensors were removed. The resulting deidentified and filtered version of the participant list in .csv format is provided in this folder.

```{r, echo = F, warning = F, message = F}

library(rio) # install.packages("rio")

all_speakers <-rio::import("File Inventories.xlsx")

```

# Filter Participants

The master participant list was already uploaded to this Rmd file. We first identified the participants who have all three timepoint recordings from the larger Co-Articulation Database. Then, we filtered out participants based on their age (only including participants who are over 45 years old). The code block below shows a more detailed look at our filtering process.

```{r, warning = F, message = F}

# Loading Needed Packages
library(tidyverse) # install.packages("tidyverse")
library(janitor) # install.packages("janitor")
library(gt) # install.packages("gt")
library(gtsummary) # install.packages("gtsummary")

speakers_final <- all_speakers %>%
  # cleaning variable names in df
  janitor::clean_names() %>%
  # selecting needed variables
  dplyr::select(c(sub_number , group, sex, age, caterpillar_no_sensors, caterpillar_conversational, caterpillar_end_no_sensors)) %>%
  # filtering out participants who do not have all three recordings
  dplyr::filter_at(vars(caterpillar_no_sensors, 
                        caterpillar_conversational, caterpillar_end_no_sensors),
                   all_vars(!is.na(.))) %>%
  # Sub21 does not have audio files, so we removed them here too
  dplyr::filter(age != "*") %>%
  # Sub49 and Sub55 have two recorded files. So we are filtering out their duplicate record
  dplyr::filter(sub_number != "Sub49" & sub_number != "Sub55*") %>%
  # Now we only want to keep participants who are over 45 years old
  dplyr::filter(age >= 45) %>%
  # Making our age variable numeric 
  dplyr::mutate(age = as.numeric(age),
                group = as.factor(group),
                sex = as.factor(sex))

# Sub 46 and Sub 62 have the wrong file names for caterpillar_end_no_sensors. That is fixed here

speakers_final <- speakers_final %>%
  dplyr::mutate(caterpillar_end_no_sensors = case_when(
    caterpillar_end_no_sensors == "Sub46_1_010_sync" ~ "Sub46_1_011_sync",
    caterpillar_end_no_sensors == "Sub62_1_010_sync" ~ "Sub62_1_011_sync",
    TRUE ~ caterpillar_end_no_sensors))

```

# Participant Descriptives

In this next block of code, we calculated some basic descriptive information for our speakers.

```{r, warning = F, message = F}

speakers_final %>%
  dplyr::select(group:age) %>%
  tbl_summary(by = group,
              statistic = list(all_categorical() ~ "{n} ({p}%)", 
                               all_continuous() ~ "{mean} ({sd})"),
              label = list(sex ~ "Sex",
                            age ~ "Age"),
              digits = list(everything() ~ c(2)))


```


```{r, eval = F, warning = F, message = F}

# export final participant list
rio::export(speakers_final, "Sensor_Effects_Participants_Lab_Version.csv")

# export demographic information. shareable version

speaker_demo <- speakers_final %>%
  dplyr::select(sub_number, group, sex, age)

rio::export(speaker_demo, "participant_demographics.csv")

```


