---
title: "Sensor Effects Analysis"
author: "Micah Hirsch"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

The following report documents the data analysis conducted for the sensor effects project.

All data analyses were conducted using R version 4.3.2.

```{r}

# Loading in the needed packages and data
library(rio) # install.packages("rio") 
library(tidyverse) # install.packages("tidyverse")
library(geometry) # install.packages("geometry")
library(patchwork) # install.packages("patchwork")
library(NatParksPalettes) # install.packages("NatParksPalettes")
library(glmmTMB) # install.packages("glmmTMB")
library(emmeans) # install.packages("emmeans")
library(lme4) # install.packages("lme4")
library(lmerTest) # install.packages("lmerTest")
library(gt) # install.packages("gt")
library(gtsummary) # install.packages("gtsummary")
library(sjPlot) # install.packages("sjPlot")

vowels <- rio::import("vowel_measures.csv") |>
  dplyr::mutate(time_point = factor(time_point, levels = c("before", "sensors", "after")),
                group = factor(group, levels = c("Control", "PD")),
                sex = factor(sex, levels = c("Male", "Female")),
                vowel = factor(vowel, levels = c("i", "u", "ae", "a")),
                seg_type = factor(seg_type, levels = c("initial", "intrarater", "interrater")))

consonants <- rio::import("consonant_measures.csv") |>
   dplyr::mutate(time_point = factor(time_point, levels = c("before", "sensors", "after")),
                group = factor(group, levels = c("Control", "PD")),
                sex = factor(sex, levels = c("Male", "Female")),
                consonant = factor(consonant, levels = c("s", "sh")),
                seg_type = factor(seg_type, levels = c("initial", "intrarater", "interrater")))

artic_rate <- rio::import("articulation_rate.csv") |>
  dplyr::mutate(time_point = factor(time_point, levels = c("before", "sensors", "after")),
                group = factor(group, levels = c("Control", "PD")), 
                sex = factor(sex, levels = c("Male", "Female")),
                phrase = as.factor(phrase),
                seg_type = factor(seg_type, levels = c("initial", "intrarater", "interrater")))

speakers <- artic_rate |>
  dplyr::select(speaker_id, group, sex, age) |>
  dplyr::distinct()

```


# Articulation Rate

## Reliability

### Interrater Reliability

```{r}

artic_rate_rel <- artic_rate |>
  tidyr::pivot_wider(names_from = seg_type,
                     values_from = artic_rate)

ar_inter <- artic_rate_rel |>
  dplyr::select(-intrarater) |>
  dplyr::filter(!is.na(interrater))

cor.test(ar_inter$initial, ar_inter$interrater, method = "pearson", use = "complete.obs")

```

### Intrarater Reliability

```{r}

ar_intra <- artic_rate_rel |>
  dplyr::select(-interrater) |>
  dplyr::filter(!is.na(intrarater))

cor.test(ar_intra$initial, ar_intra$intrarater, method = "pearson", use = "complete.obs")

```

```{r}

rm(ar_inter, ar_intra, artic_rate_rel)

```


## Descriptives

```{r}

ar_des <- artic_rate |>
  dplyr::filter(seg_type == "initial") |>
  dplyr::group_by(speaker_id, time_point) |>
  dplyr::summarize(artic_rate_m = mean(artic_rate)) |>
  dplyr::left_join(speakers, by = "speaker_id")

```


## Plot

```{r}

my_pal <- natparks.pals("Denali", 6)

overall_ar <- ar_des |>
  dplyr::group_by(group, time_point) |>
  dplyr::summarize(artic_rate = mean(artic_rate_m), sd = sd(artic_rate_m), se = sd/sqrt(n())) |>
  dplyr::ungroup()

artic_rate_plot <- overall_ar |>
  ggplot() +
  aes(x = time_point,
      y = artic_rate,
      color = group,
      group = group) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = artic_rate - se, ymax = artic_rate + se)) +
  labs(x = "Time Point",
       y = "Articulation Rate (syl/s)") +
  scale_color_manual(values = c(my_pal[1], my_pal[4])) +
  theme_classic()

artic_rate_plot

```

## Model

### Model Summary

```{r}

ar_model <- lmer(artic_rate_m ~ time_point*group + (1|speaker_id), data = ar_des)
summary(ar_model)

sjPlot::tab_model(ar_model)

```


### Pairwise Comparisons

```{r}

emm_artic_rate <- emmeans(ar_model, specs = pairwise ~ time_point:group)
emm_artic_rate$contrasts

```

```{r}

rm(ar_model, ar_des, emm_artic_rate, overall_ar)

```


# Vowel Space Area

## Reliability

### Interrater Reliability

```{r}

VSA_coords <- vowels |>
  dplyr::group_by(speaker_id, time_point, vowel, seg_type) |>
  dplyr::summarize(F1 = mean(f1),
                   F2 = mean(f2)) |>
  dplyr::ungroup()

VSA <- VSA_coords |>
  dplyr::group_by(speaker_id, time_point, seg_type) |>
  dplyr::mutate(VSA = (geometry::polyarea(F1, F2))/1000) |> # Converted to kHz
  dplyr::select(!c(vowel, F1, F2)) |>
  dplyr::distinct() |>
  dplyr::left_join(speakers, by = "speaker_id")

VSA_rel <- VSA |>
  tidyr::pivot_wider(names_from = seg_type,
                     values_from = VSA)

VSA_inter <- VSA_rel |>
  dplyr::select(-intrarater) |>
  dplyr::filter(!is.na(interrater))

cor.test(VSA_inter$initial, VSA_inter$interrater, method = "pearson", use = "complete.obs")

```
### Intrarater Reliability

```{r}

VSA_intra <- VSA_rel |>
  dplyr::select(-interrater) |>
  dplyr::filter(!is.na(intrarater))

cor.test(VSA_intra$initial, VSA_intra$intrarater, method = "pearson", use = "complete.obs")

```

```{r}

rm(VSA_rel, VSA_intra, VSA_inter, VSA_coords)

```


## Descriptives

```{r}

VSA_mod <- VSA |>
  dplyr::filter(seg_type == "initial")

```


## Plot

```{r}

VSA_overall <- VSA_mod |>
  dplyr::group_by(group, time_point) |>
  dplyr::summarize(VSA_mean = mean(VSA), VSA_sd = sd(VSA), se = VSA_sd/sqrt(n()))

VSA_plot <- VSA_overall |>
  ggplot() +
  aes(x = time_point,
      y = VSA_mean,
      group = group,
      color = group) +
  geom_point() +
  geom_line() +
  geom_errorbar(
    aes(
      ymin = VSA_mean - se,
      ymax = VSA_mean + se),
    width = .1
    ) +
  scale_color_manual(values = c(my_pal[1], my_pal[4])) +
  labs(
    x = "",
    y = bquote('Vowel Space Area '(kHz^2))) +
  theme_classic() +
  theme(aspect.ratio = 1)

VSA_plot

```

## Model

### Model Summary

```{r}

VSA_model <- lmer(VSA ~ time_point*group + (1|speaker_id), data = VSA_mod)
summary(VSA_model)

sjPlot::tab_model(VSA_model)

```

# Spectral Moment Analysis

## Reliability

### Interrater Reliability

M1

```{r}

moment_mod <- consonants |>
  dplyr::select(speaker_id, group, sex, age, time_point, seg_type, consonant, m1, m2) |>
  dplyr::group_by(speaker_id, time_point, consonant, seg_type) |>
  dplyr::summarize(M1 = mean(m1), M2 = mean(m2)) |>
  dplyr::ungroup() |>
  dplyr::left_join(speakers, by = "speaker_id")
  

M1_rel <- moment_mod|>
  dplyr::select(speaker_id, group, sex, age, time_point, seg_type, consonant, M1) |>
  tidyr::pivot_wider(names_from = seg_type,
                     values_from = M1)


M1_inter <- M1_rel |>
  dplyr::select(-intrarater) |>
  dplyr::filter(!is.na(interrater))

cor.test(M1_inter$initial, M1_inter$interrater, method = "pearson", use = "complete.obs")

```
M2

```{r}

M2_rel <- moment_mod|>
  dplyr::select(speaker_id, group, sex, age, time_point, seg_type, consonant, M2) |>
  tidyr::pivot_wider(names_from = seg_type,
                     values_from = M2)


M2_inter <- M2_rel |>
  dplyr::select(-intrarater) |>
  dplyr::filter(!is.na(interrater))

cor.test(M2_inter$initial, M2_inter$interrater, method = "pearson", use = "complete.obs")

```


### Intrarater

M1

```{r}

M1_intra <- M1_rel |>
  dplyr::select(-interrater) |>
  dplyr::filter(!is.na(intrarater))

cor.test(M1_intra$initial, M1_intra$intrarater, method = "pearson", use = "complete.obs")

```

M2

```{r}

M2_intra <- M2_rel |>
  dplyr::select(-interrater) |>
  dplyr::filter(!is.na(intrarater))

cor.test(M2_intra$initial, M2_intra$intrarater, method = "pearson", use = "complete.obs")

```

## Descriptives

```{r}


```


## Plot

```{r}



```

