---
title: "Sensor Effects: Data Prep"
author: "Austin Thompson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This script contains the preliminary data processing for the sensor effects project. The preliminary results presented here are for a proposal submitted to the 2024 Conference of Motor Speech.

# Packages
```{r}
library(rio)
library(tidyverse)
library(rPraat) # install.packages('rPraat')
library(devtools) # install.packages('devtools')
library(PraatR) # devtools:::install_github("usagi5886/PraatR")
```

# Loading in the data
```{r}

rawDataPath <- "/Users/austinthompson/Library/CloudStorage/Dropbox/Work/Research/Github/Sensor-Effects-Project/Data Analysis/Raw Data"
databasePath <- "/Users/austinthompson/Library/CloudStorage/Dropbox/Work/Research/Databases/Coartic-Database"

## Segmented Data (i.e., Speakers that are completed)
segmentedData <- list.files(
  path = rawDataPath, # get the names of the completed speakers from the files
  ) %>%
  as.data.frame() %>%
  dplyr::rename(SpeakerID = 1)

## Import Speaker information
speakers <- rio::import("participant_demographics.csv") %>%
  dplyr::select(1:4) %>%
  dplyr::rename(SpeakerID = 1) %>%
  # Filter out participants who are not completed (do not have a folder in Dropbox)
  dplyr::filter(
    .$SpeakerID %in% segmentedData$SpeakerID
  ) 
rm(segmentedData)


loadData <- function(path, speaker) {
  
  path_tp_info <- path %>%
    as.data.frame() %>%
    dplyr::rename(path = 1) %>%
    
    # Finding which TP we have
    dplyr::mutate(tp = case_when(
      grepl(pattern = "before", ignore.case = T, path) ~ "before",
      grepl(pattern = "after", ignore.case = T, path) ~ "after",
      grepl(pattern = "sensor", ignore.case = T, path) ~ "sensors",
    ))
  
   # Load the TextGrid
  tg <- rPraat::tg.read(fileNameTextGrid = path,
                          encoding = "UTF-8")
  
  Phrase <- cbind(tg[[1]][["label"]],tg[[1]][["t1"]], tg[[1]][["t2"]]) %>%
    as.data.frame() %>%
    dplyr::rename(
      Segment = 1,
      onset = 2,
      offset = 3) %>%
    dplyr::mutate(
      Segment = gsub(pattern = " ",
                     replacement = "",
                     x = Segment),
      onset = as.numeric(onset),
      offset = as.numeric(offset)) %>%
      dplyr::filter(Segment != "")
  
  Phoneme <- cbind(tg[[2]][["label"]],tg[[2]][["t1"]], tg[[2]][["t2"]]) %>%
    as.data.frame() %>%
    dplyr::rename(
      Segment = 1,
      onset = 2,
      offset = 3) %>%
    dplyr::mutate(
      Segment = gsub(pattern = " ",
                     replacement = "",
                     x = Segment),
      onset = as.numeric(onset),
      offset = as.numeric(offset)) %>%
    dplyr::filter(Segment != "")
  
  speakerSegments <- rbind(Phrase, Phoneme) %>%
    dplyr::mutate(timePoint = path_tp_info$tp,
                  path = path_tp_info$path)
  
  return(speakerSegments)
  rm(Phrase, Phoneme)
}


k <- 1
while (k <= nrow(speakers)) {
  
  speaker <- speakers$SpeakerID[k]
  file_path <- paste(rawDataPath, speaker, sep = "/")

  speakerFiles <- list.files(
    path = paste0(file_path,"/")) %>%
    as.data.frame() %>%
    dplyr::rename(File = 1) %>%
    dplyr::filter(grepl(
      pattern = ".TextGrid",
      x = File
    )) %>%
    dplyr::mutate(
      path = paste(file_path, File, sep = "/")
    )
  
  speakerSegments <- base::do.call(rbind,lapply(speakerFiles$path,loadData, speaker = speaker)) %>%
    dplyr::mutate(SpeakerID = speaker)
  
  # Initializing the Segments
  if (k == 1) {
    Segments <- speakerSegments %>%
      dplyr::relocate(SpeakerID, .before = "Segment")
  } else {
    Segments <- rbind(Segments, speakerSegments)
  }
  rm(speakerSegments)
  
  k <- k + 1
}

Segments <- Segments %>%
  dplyr::mutate(
    # Correcting a human coding error
    Segment = case_when(
      Segment == "Phrase_3.2_9" ~ "Phrase3.2_9",
      Segment == "Phase3.3_10" ~ "Phrase3.3_10",
      TRUE ~ Segment)) %>%
  
  # Merge with the speaker list, which has the demographics
  base::merge(., speakers) %>%
  dplyr::relocate(c(Group:Age,path, timePoint), .before = Segment) %>%
  dplyr::select(!path)

# Pulling out the phrases
phrases <- Segments %>%
  dplyr::filter(grepl(pattern = "phrase",
                      ignore.case = T,
                      x = Segment)) %>%
  dplyr::mutate(
    Phrase = case_when(
      grepl(pattern = "Phrase1", x = Segment) ~ "Phrase 1",
      grepl(pattern = "Phrase2", x = Segment) ~ "Phrase 2",
      grepl(pattern = "Phrase3", x = Segment) ~ "Phrase 3",
      ),
    Syllables = sub(".*_", "", Segment),
    Syllables = as.numeric(Syllables))

phonemes <- Segments %>%
    dplyr::filter(!grepl(pattern = "phrase",
                      ignore.case = T,
                      x = Segment))


```

# Loading in the audio recordings
```{r}
fileInventories <- rio::import(
  file = paste(databasePath, "File Inventories.xlsx", sep = "/")
) %>%
  
  # Cleaning up File Inventories
  dplyr::rename(SpeakerID = 1) %>%
  
  # Getting just the completed & segmented speakers
  dplyr::filter(.$SpeakerID %in% speakers$SpeakerID) %>%
  
  # Selecting just the cols of interest
  dplyr::select(SpeakerID,
                `Folder #1`,
                `Caterpillar (No Sensors)`,
                `Folder 2`,
                `Caterpillar (Conversational)`,
                `Caterpillar (End, No Sensors)`) %>%
  
  # Creating the path names
  dplyr::mutate(
    path = paste(databasePath, SpeakerID, sep = "/"),
    before = paste(path,`Folder #1`, `Caterpillar (No Sensors)`, sep = "/"),
    sensors = paste(path, `Folder 2`, `Caterpillar (Conversational)`, sep = "/"),
    after = paste(path, `Folder 2`, `Caterpillar (End, No Sensors)`, sep = "/"),
  ) %>%
  
  # Pivoting longer
  dplyr::select(SpeakerID, before, sensors, after) %>%
  tidyr::pivot_longer(cols = c(before:after),
                      names_to = "timePoint",
                      values_to = "filePath")


```

# Calculating Measures

## Consonant Measures
```{r}
consonants <- phonemes %>%
  dplyr::filter(Segment == "sh" | Segment == "s") %>%
  base::merge(., fileInventories) %>%
  dplyr::mutate(Row = dplyr::row_number())

# Loop to calculate M1 & M2
k <- 1
while (k <= nrow(consonants)) {
  
  targetFile <- consonants %>%
    dplyr::filter(row_number() == k) %>%
    dplyr::select(filePath) %>%
    as.character()
  
  currentTarget <- consonants %>%
    dplyr::mutate(onset = onset,
                  offset = offset) %>%
    slice(k)
  
  # Loading in the sound wav
  sndWav <- rPraat::snd.read(paste0(targetFile, ".wav"))
  
  # Cutting the sound wav to be just the target
  rPraat::snd.cut(sndWav,
                Start = currentTarget$onset,
                End = currentTarget$offset) %>%
  rPraat::snd.write(.,paste0(targetFile,"_target.wav"))
  
  # Creating the current target.Spectrum
  PraatR::praat( "To Spectrum...",
                 arguments = list(TRUE),
                 input = paste0(targetFile,"_target.wav"),
                 output = paste0(targetFile,"_target.Spectrum"),
                 filetype="binary",
                 overwrite=TRUE)
  
  
consonants <- consonants %>%
      filter(Row == k) %>%
      dplyr::mutate(
        M1 = PraatR::praat( "Get centre of gravity...",
                            arguments = list(1),
                            input = paste0(targetFile,"_target.Spectrum")) %>%
                      str_replace(" hertz", "") %>%
                      as.numeric() / 1000,
        M2 = PraatR::praat( "Get standard deviation...",
                            arguments = list(1),
                            input = paste0(targetFile,"_target.Spectrum")) %>%
                      str_replace(" hertz", "") %>%
                      as.numeric() / 1000,
        # Spectral moment power distribution
        M1_p = PraatR::praat( "Get centre of gravity...",
                            arguments = list(2),
                            input = paste0(targetFile,"_target.Spectrum")) %>%
                      str_replace(" hertz", "") %>%
                      as.numeric() / 1000,
        M2_p = PraatR::praat( "Get standard deviation...",
                            arguments = list(2),
                            input = paste0(targetFile,"_target.Spectrum")) %>%
                      str_replace(" hertz", "") %>%
                      as.numeric() / 1000) %>%
      bind_rows(., consonants %>%
                  filter(Row != k)) %>%
      arrange(Row)

# Cleaning up the folder
file.remove(paste0(targetFile,"_target.wav"))
file.remove(paste0(targetFile,"_target.Spectrum"))

k <- k + 1
}

consonants <- consonants %>%
  dplyr::select(!c(filePath, Row))

dir.create(path = "Prepped Data",
           showWarnings = F)
rio::export(
  x = consonants,
  file = "Prepped Data/FinalMeasures_consonants.csv"
)
```

## Vowel Measures
```{r}
vowels <- phonemes %>%
  dplyr::filter(Segment != "sh") %>%
  dplyr::filter(Segment != "s") %>%
  base::merge(., fileInventories) %>%
  dplyr::mutate(Row = dplyr::row_number(),
                label = Segment,
                vowel = gsub(
                  pattern = "l",
                  replacement = "",
                  x = label
                ),
                vowel = base::tolower(vowel))

# Loop to calculate F1 & F2 at temporal midpoint
k <- 1
while (k <= nrow(vowels)) {
  
  targetFile <- vowels %>%
    dplyr::filter(row_number() == k) %>%
    dplyr::select(filePath) %>%
    as.character()
  
  currentTarget <- vowels %>%
    dplyr::mutate(onset = onset,
                  offset = offset) %>%
    slice(k)
  
  # Loading in the sound wav
  sndWav <- rPraat::snd.read(paste0(targetFile, ".wav"))
  
  # Cutting the sound wav to be just the target
  rPraat::snd.cut(sndWav,
                Start = currentTarget$onset,
                End = currentTarget$offset) %>%
  rPraat::snd.write(.,paste0(targetFile,"_target.wav"))
  
  # Creating the current target.Formant
  formantArg <- list(
    .00,
    5.0,
    ifelse(currentTarget$Sex == "M", 5000, 5500),
    0.025,
    50
  )
  PraatR::praat( "To Formant (burg)...",
                 arguments = formantArg,
                 input = paste0(targetFile,"_target.wav"),
                 output = paste0(targetFile,"_target.Formant"),
                 filetype="text",
                 overwrite=TRUE)
  
  formants <- rPraat::formant.read(
    fileNameFormant = paste0(targetFile,"_target.Formant"),
    encoding = "auto"
    )
  midFrame <- rPraat::formant.getPointIndexNearestTime(formants,
                                   time = (formants$xmax/2) + formants$xmin)
  
  midpoint <- formants$frame[[midFrame]][["frequency"]] %>%
    as.data.frame() %>%
    dplyr::rename(Formants = 1)
  
  F1_mid <- midpoint[1,]
  F2_mid <- midpoint[2,]
  
vowels <- vowels %>%
      filter(Row == k) %>%
      dplyr::mutate(
        F1 = as.numeric(F1_mid),
        F2 = as.numeric(F2_mid)) %>%
      bind_rows(., vowels %>%
                  filter(Row != k)) %>%
      arrange(Row)

# Cleaning up the folder
file.remove(paste0(targetFile,"_target.wav"))
file.remove(paste0(targetFile,"_target.Formant"))

k <- k + 1
}

vowels <- vowels %>%
  dplyr::select(!c(filePath, Row))

dir.create(path = "Prepped Data",
           showWarnings = F)
rio::export(
  x = vowels,
  file = "Prepped Data/FinalMeasures_vowels.csv"
)

```

## Prosody Measures
```{r}
articRate <- phrases %>%
  dplyr::mutate(duration = offset - onset,
                articRate = Syllables/duration)

dir.create(path = "Prepped Data",
           showWarnings = F)
rio::export(
  x = articRate,
  file = "Prepped Data/FinalMeasures_articRate.csv"
)
```

# Visualizations
## Cosonnants
```{r}
plotData <- rio::import(
  file = "Prepped Data/FinalMeasures_consonants.csv"
)

plotData %>%
  dplyr::group_by(Group, timePoint, Segment) %>%
  dplyr::summarise(M1 = mean(M1),
                   M1_p = mean(M1_p),
                   M2 = mean(M2),
                   M2_p = mean(M2_p)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(timePoint = factor(timePoint, levels = c("before",
                                                         "sensors",
                                                         "after"))) %>%
  ggplot() +
  aes(x = timePoint,
      y = M1,
      color = Group,
      group = Group) +
  geom_line(color = "grey") +
  geom_point() +
  labs(x = "Timepoint") +
  facet_wrap(~Segment) +
  theme_classic()

dir.create(
  path = "Figures",
  showWarnings = F
)

ggsave(
  filename = "Figures/Results_consonants.png",
  plot = last_plot(),
  height = 4,
  width = 6,
  units = "in",
  scale = 1
)
```

## Vowels
```{r}
plotData <- rio::import(
  file = "Prepped Data/FinalMeasures_vowels.csv"
)

plotData %>%
  dplyr::group_by(Group, timePoint, vowel) %>%
  dplyr::summarise(
    F1 = mean(F1),
    F2 = mean(F2),
    ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(timePoint = factor(timePoint, levels = c("before",
                                                         "sensors",
                                                         "after"))) %>%
  ggplot() +
  aes(x = F2,
      y = F1,
      color = vowel,
      group = Group,
      shape = timePoint) +
  #geom_line(color = "grey") +
  geom_point() +
  scale_x_reverse() +
  scale_y_reverse() +
  facet_wrap(~Group) +
  labs(shape = "Timepoint",
       color = "Vowel") +
  theme_classic()

dir.create(
  path = "Figures",
  showWarnings = F
)

ggsave(
  filename = "Figures/Results_vowels.png",
  plot = last_plot(),
  height = 4,
  width = 6,
  units = "in",
  scale = 1
)
```

## Artic Rate
```{r}
plotData <- rio::import(
  file = "Prepped Data/FinalMeasures_articRate.csv"
)

plotData %>%
  dplyr::group_by(Group, timePoint) %>%
  dplyr::summarise(articRate = mean(articRate)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(timePoint = factor(timePoint, levels = c("before",
                                                         "sensors",
                                                         "after"))) %>%
  ggplot() +
  aes(x = timePoint,
      y = articRate,
      color = Group,
      group = Group) +
  geom_line(color = "grey") +
  geom_point() +
  labs(x = "Timepoint",
       y = "Articulation Rate (syl/s)") +
  theme_classic()

dir.create(
  path = "Figures",
  showWarnings = F
)

ggsave(
  filename = "Figures/Results_articRate.png",
  plot = last_plot(),
  height = 4,
  width = 6,
  units = "in",
  scale = 1
)

```

