---
title: "Sensor_Effects_Preliminary_Analysis"
author: "Micah E. Hirsch"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

The purpose of this document is to conduct preliminary analyses for the Sensor Effects project. The primary analyses conducted here are descriptive statistics and data visualizations.

```{r}

library(rio)
library(tidyverse)
library(geometry) # install.packages('geometry')
library(ggpubr)
library(NatParksPalettes) # install.packages('NatParksPalettes')

artic_rate_df <- rio::import("Prepped Data/FinalMeasures_articRate.csv")
consonants_df <- rio::import("Prepped Data/FinalMeasures_consonants.csv")
vowels_df <- rio::import("Prepped Data/FinalMeasures_vowels.csv")

```

# Descriptive Statistics

## Participant Demographics by Group

```{r}

participants <- artic_rate_df %>%
  dplyr::select(SpeakerID, Group, Sex, Age) %>%
  dplyr::distinct()

participants %>%
  dplyr::group_by(Group, Sex) %>%
  dplyr::summarize(Age = mean(Age))

```


## Overall Participant Demographics

```{r}

participants %>%
  dplyr::summarize(mean_age = mean(Age), sd = sd(Age), 
                   min_age = min(Age), max = max(Age))

```

## Articulation Rate

```{r}

artic_descriptives <- artic_rate_df %>%
  dplyr::group_by(SpeakerID, timePoint) %>%
  dplyr::summarize(articRate = sum(Syllables)/sum(duration)) %>%
  dplyr::left_join(participants, by = "SpeakerID")

overall_articRate <- artic_descriptives %>%
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = fct_relevel(timePoint, "before", "sensors", "after")) %>%
  dplyr::group_by(Group, timePoint) %>%
  dplyr::summarize(artic_rate = mean(articRate), sd = sd(articRate), se = sd/sqrt(n())) %>%
  dplyr::ungroup()

artic_rate_plot <- overall_articRate %>%
  ggplot() +
  aes(x = timePoint,
      y = artic_rate,
      color = Group,
      group = Group) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = artic_rate - se, ymax = artic_rate + se)) +
  labs(x = "Time Point",
       y = "Articulation Rate (syl/s)") +
  theme_classic()
  
  
artic_rate_plot
  

```

## F1 and F2 Range

```{r}

F1_F2<- vowels_df %>%
  tidyr::pivot_longer(cols = F1:F2,
                      names_to = "Formant",
                      values_to = "Hz") %>%
  dplyr::group_by(SpeakerID, timePoint, Formant) %>%
  dplyr::summarize(Min = min(Hz), Max = max(Hz)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(range = Max - Min) %>%
  dplyr::left_join(participants, by = "SpeakerID")


F1_F2_des <- F1_F2 %>%
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = fct_relevel(timePoint, "before", "sensors", "after")) %>%
  dplyr::group_by(Group, timePoint, Formant) %>%
  dplyr::summarize(mean_range = mean(range), sd = sd(range)) %>%
  dplyr::ungroup()

F1_F2_plot <- F1_F2_des %>%
  ggplot() +
  aes(x = timePoint,
      y = mean_range,
      group = Group,
      color = Group) +
  geom_line() +
  geom_point() +
  labs(x = "Time Point",
       y = "Hz Range") +
  facet_wrap("Formant") +
  theme_classic()

F1_F2_plot
  

```
## VSA

```{r}
pal <- natparks.pals("Arches", 9, type = "discrete") %>%
  as.data.frame() %>%
  t() %>%
  as.data.frame() %>%
  dplyr::select(V2,V8) %>%
  as.character()


VSA_coords <- vowels_df %>%
  dplyr::group_by(SpeakerID, timePoint, vowel) %>%
  dplyr::summarize(mean_F1 = mean(F1),
                   mean_F2 = mean(F2))

VSA_measure <- VSA_coords %>%
  dplyr::mutate(VSA = (geometry::polyarea(mean_F1, mean_F2))/1000) %>% # Converted this into kHz for smaller units
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = factor(timePoint,
                                   levels = c("before", "sensors", "after"),
                                   labels = c("Before", "Sensors", "After"))) %>%
  dplyr::left_join(participants, by = "SpeakerID") %>%
  dplyr::select(!vowel:mean_F2) %>%
  dplyr::distinct() %>%
  dplyr::ungroup()

VSA_plot <- VSA_measure %>% 
  dplyr::group_by(Group, timePoint) %>%
  dplyr::summarize(VSA_mean = mean(VSA), VSA_sd = sd(VSA), se = VSA_sd/sqrt(n())) 

plot_VSA <- VSA_plot %>%
  ggplot() +
  aes(x = timePoint,
      y = VSA_mean,
      group = Group,
      color = Group) +
  geom_point() +
  geom_line() +
  geom_errorbar(
    aes(
      ymin = VSA_mean - se,
      ymax = VSA_mean + se),
    width = .1
    ) +
  scale_color_manual(values = pal) +
  labs(
    x = "",
    y = bquote('Vowel Space Area '(kHz^2))) +
  theme_classic() +
  theme(aspect.ratio = 1)

plot_VSA

ggsave("VSA_plot.png", plot = last_plot())

```


## Moment Analysis

### M1

```{r}

M1_des <- consonants_df %>%
  dplyr::select(c(SpeakerID, timePoint, Group, Sex, Segment, M1, M2)) %>%
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = factor(timePoint,
                                   levels = c("before", "sensors", "after"),
                                   labels = c("Before", "Sensors", "After")),
                Segment = factor(Segment,
                                 levels = c("s", "sh"),
                                 labels = c("/s/", "/ʃ/"))) %>%
  dplyr::group_by(Group, timePoint, Segment) %>%
  dplyr::summarize(Mean_M1 = mean(M1), sd = sd(M1), se = sd/sqrt(n()))

M1_plot <- M1_des %>%
  ggplot() +
  aes(x = timePoint,
      y = Mean_M1,
      group = Group,
      color = Group) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = Mean_M1 - se, ymax = Mean_M1 + se), width = 0.1) +
  labs(x = "",
       y = "M1 (kHz)") +
  scale_color_manual(values = pal) +
  facet_wrap("Segment") +
  theme_classic() +
  theme(aspect.ratio = 1)

M1_plot

```

### M2

```{r}

M2_des <- consonants_df %>%
  dplyr::select(c(SpeakerID, timePoint, Group, Sex, Segment, M1, M2)) %>%
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = fct_relevel(timePoint, "before", "sensors", "after")) %>%
  dplyr::group_by(Group, timePoint, Segment) %>%
  dplyr::summarize(Mean_M2 = mean(M2), sd = sd(M2), se = sd/sqrt(n()))

M2_plot <- M2_des %>%
  ggplot() +
  aes(x = timePoint,
      y = Mean_M2,
      group = Group,
      color = Group) +
  geom_line() +
  geom_errorbar(aes(ymin = Mean_M2 - se, ymax = Mean_M2 + se), width = 0.2) +
  labs(x = "Time Point",
       y = "M2 (kHz)") +
  facet_wrap("Segment") +
  theme_classic()

M2_plot

```

# M1 Ratio

```{r}

M1_ratio <- consonants_df %>%
  dplyr::select(SpeakerID, timePoint, Group, Sex, Age, Segment, M1) %>%
  tidyr::pivot_wider(names_from = Segment,
                     values_from = M1) %>%
  dplyr::mutate(M1_ratio = s/sh)

M1_ratio_des <- M1_ratio %>%
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = fct_relevel(timePoint, "before", "sensors", "after")) %>%
  dplyr::group_by(Group, timePoint) %>%
  dplyr::summarize(M1_ratio_mean = mean(M1_ratio), sd = sd(M1_ratio), se = sd/sqrt(n()))

M1_ratio_plot <- M1_ratio_des %>%
  ggplot() +
  aes(x = timePoint,
      y = M1_ratio_mean,
      group = Group,
      color = Group) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = M1_ratio_mean - se, ymax = M1_ratio_mean + se)) +
  labs(x = "Time Point",
       y = "M1 Ratio s/sh") +
  theme_classic()

M1_ratio_plot

ggsave("Figures/M1_ratio.png", plot = last_plot())

```

# M2 Ratio

```{r}

M2_ratio <- consonants_df %>%
  dplyr::select(SpeakerID, timePoint, Group, Sex, Age, Segment, M2) %>%
  tidyr::pivot_wider(names_from = Segment,
                     values_from = M2) %>%
  dplyr::mutate(M2_ratio = s/sh)

M2_ratio_des <- M2_ratio %>%
  dplyr::mutate(timePoint = as.factor(timePoint),
                timePoint = fct_relevel(timePoint, "before", "sensors", "after")) %>%
  dplyr::group_by(Group, timePoint) %>%
  dplyr::summarize(M2_ratio_mean = mean(M2_ratio), sd = sd(M2_ratio), se = sd/sqrt(n()))

M2_ratio_plot <- M2_ratio_des %>%
  ggplot() +
  aes(x = timePoint,
      y = M2_ratio_mean,
      group = Group,
      color = Group) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = M2_ratio_mean - se, ymax = M2_ratio_mean + se)) +
  labs(x = "Time Point",
       y = "M2 Ratio s/sh") +
  theme_classic()

M2_ratio_plot

ggsave("Figures/M2_ratio.png", plot = last_plot())

```

# MSC Plot

```{r}

msc_plot <- M1_plot + plot_VSA +
  patchwork::plot_layout(
    ncol = 2,
    nrow = 1,
    widths = c(2, 1),
    guides = "collect")

msc_plot

ggsave("msc_plot.png", plot = last_plot(), width = 5.5, height = 2, units = "in", scale = 1.5)

```

